EGGs are adhesive!

### 2025-03-04 calco/main.tex
roba per string diagrams

\begin{example}\label[example]{exa_3}
	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature where $O_\Sigma =  \{n, x, *, /\}$, where $n$ is any natural number and $x$ is any variable,
	and $\ari_\Sigma(n)=\ari_\Sigma(x) = 0$, $\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then, $\mathcal{G}^\Sigma$ can be depicted as
	\begin{center}
		\begin{tikzpicture}
			\begin{pgfonlayer}{nodelayer}
				\node[style=node] (v) at (0, 0){};
				\node[style=none] (vlab) at (0, -0.4){$v$};

@@

\begin{example}\label[example]{lab_2}
	Take again $\Sigma_G$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
	\[\begin{matrix}
		a=f(h_1) & 2=f(h_2) & *=f(h_3) & / =f(h_4)
	\end{matrix}\]
	In this case we get the following picture

>>>>

\begin{example}\label[example]{exa_3}
	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature with $O_\Sigma =  \{n, a, *, /\}$, where $n$ is any natural number and $a$ is any variable,
	and $\ari_\Sigma(n)=\ari_\Sigma(x) = 0$, $\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then, $\mathcal{G}^\Sigma$ can be depicted as
	\begin{center}
		\begin{tikzpicture}
			\begin{pgfonlayer}{nodelayer}
				\node[style=node] (v) at (0, 0){};
				\node[style=none] (vlab) at (0, -0.4){$v$};

@@

\begin{example}\label[example]{lab_2}
	Take again $\Sigma$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
	\[\begin{matrix}
		a=f(h_1) & 2=f(h_2) & *=f(h_3) & / =f(h_4)
	\end{matrix}\]
	In this case we get the following picture
